---
title: "COVID Report"
#author: "Juan Carlos LaGuardia"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
    includes:
      after_body: footer.html
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggthemes)
library(formattable)
library(gridExtra)
library(lubridate)
library(DT)
library(readr)
library(kableExtra)
library(timetk)
library(lubridate)
library(tidyquant)
```

## COVID update for Bay Area

**Personal Note.**  I created this just for the cities you asked for.  It seems Alameda's county data had a blip and released a whole bunch of cases all on the first of Feb.  I'm curious if they are counting previously uncounted population based on a rule change.  Whatever the reason, on Feb 2, there was an adjustment period where they all had less total than the day before and didn't report for Feb 3rd.  Long story short, mixing county data is messy, but i believe Dublin and Pleasanton are also seeing a downward trend. 

```{r read_data, include=FALSE}
city<-read_csv("/Users/d985286/california-coronavirus-data/latimes-place-totals.csv")

a1<-city %>% #filter(date < '2022-01-14') %>% 
 group_by(name) %>%
 mutate(before_score = lag(confirmed_cases, order_by=date),
        cases = confirmed_cases - before_score) %>% 
 mutate(cases = ifelse(is.na(before_score),confirmed_cases,cases),
        case_by_10k = (cases*10000)/population)
```
## Raw Counts for cities for last 7 days
```{r table1, echo=FALSE}
   a1 %>% select(name,date,cases) %>% filter(name %in% c("San Ramon","94568: Dublin","94588: Pleasanton", "94566: Pleasanton"), date > (Sys.Date() - 8)) %>%
  mutate(dates = format(date, "%m/%d")) %>% select(-date) %>% 
   group_by(name) %>% spread(dates, cases) %>% rename(City=name) %>% 
  formattable(align=c("l","c","c","c","c","c","c","c","c"))

```
## Comparable rates per 10k population across cities for last week (averaged) 
```{r table2, echo=FALSE}
   a1 %>% select(name,date,case_by_10k) %>% filter(name %in% c("San Ramon","94568: Dublin","94588: Pleasanton", "94566: Pleasanton"),date > (Sys.Date() - 8)) %>% 
 summarize(caserate=round(mean(case_by_10k),2) ) %>% 
  group_by(name) %>% rename(City=name) %>%  formattable(list(align=c("l","r"),caserate=color_bar("lightblue")))

```

```{r graph, echo=FALSE,  message=FALSE, warning=FALSE}
end <- as_date(Sys.Date())
a1 %>% filter( name %in% c("San Ramon","94568: Dublin")) %>% ggplot(aes(date,cases)) + 
        facet_wrap(~name,ncol=1)  +
        geom_ma(ma_fun = EMA, n = 7,show.legend = T,linetype = "solid") + 
        coord_x_date(xlim = c(end - weeks(85), end))  + 
        theme_tq() + xlab("") + ylab("Daily Cases") + labs(title = "COVID 19 Historical Trend",
                                      caption = "Data source: LA Times; 7 day Average")
```


```{r graph2, echo=FALSE,  message=FALSE, warning=FALSE}
end <- as_date(Sys.Date())
a1 %>% filter( date > '2021-07-01',name %in% c("San Ramon","94568: Dublin","94588: Pleasanton", "94566: Pleasanton")) %>%
  rename(City=name) %>% ggplot(aes(date,case_by_10k,col=City,group=City)) + 
        geom_ma(ma_fun = EMA, n = 7,show.legend = T,linetype = "solid") + 
        coord_x_date(xlim = c(end - weeks(12), end))  + 
        theme_tq() + xlab("") +ylab("Case Rate per 10k") + labs(title = "COVID Case Rate Comparison",
                                      caption = "Data source: LA Times; 7 day Average")
```

*List of useful websites*

* [Contra Costa County Site](https://www.coronavirus.cchealth.org/dashboard)

* [LA Times Dashboard](https://www.latimes.com/projects/california-coronavirus-cases-tracking-outbreak/)

* [New York Times Dashboard](https://www.nytimes.com/interactive/2021/us/covid-cases.html)

* [California Public Dashboard](https://public.tableau.com/views/COVID-19PublicDashboard/Covid-19Public)

* [California Department of Public Health](https://www.cdph.ca.gov/Programs/CID/DCDC/Pages/Immunization/ncov2019.aspx) Was a place to look for positivity rates

* [IHME model](https://covid19.healthdata.org/united-states-of-america/california) is a good place to go for projections, as we blend this model into our work at KP  


