---
title: "COVID Report"
#author: "Juan Carlos LaGuardia"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
    includes:
      after_body: footer.html
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggthemes)
library(formattable)
library(gridExtra)
library(lubridate)
library(DT)
library(readr)
library(kableExtra)
library(timetk)
library(lubridate)
library(tidyquant)
```

## COVID update for Bay Area

To my knowledge there isn't a good place to find out how many cases we are seeing daily (captured by first table in this document) and capturing city trends so I'm making this information a report that I generate automatically to help make decisions.  

**A couple of personal notes.**  It looks like the flow of data has been adjusted and now its coming in through today.  It looked like we were trending down, but it now seems it's still too soon to call.  Lets hope we see better trends over the weekend. 

```{r read_data, include=FALSE}
city<-read_csv("/Users/d985286/california-coronavirus-data/latimes-place-totals.csv")

a1<-city %>% #filter(date < '2022-01-14') %>% 
 group_by(name) %>%
 mutate(before_score = lag(confirmed_cases, order_by=date),
        cases = confirmed_cases - before_score) %>% 
 mutate(cases = ifelse(is.na(before_score),confirmed_cases,cases),
        case_by_10k = (cases*10000)/population)
```
## Raw Counts for cities for last 7 days
```{r table1, echo=FALSE}
   a1 %>% select(name,date,cases) %>% filter(name %in% c("Martinez","Pleasant Hill","Moraga","Orinda","Walnut Creek","Concord","Richmond"), date > (Sys.Date() - 8)) %>%
  mutate(dates = format(date, "%m/%d")) %>% select(-date) %>% 
   group_by(name) %>% spread(dates, cases) %>% rename(City=name) %>% 
  formattable(align=c("l","c","c","c","c","c","c","c","c"))

```
## Comparable rates per 10k population across cities for last week (averaged) 
```{r table2, echo=FALSE}
   a1 %>% select(name,date,case_by_10k) %>% filter(name %in% c("Martinez","Pleasant Hill","Moraga","Orinda","Walnut Creek","Concord","Richmond","Kensington"),date > (Sys.Date() - 8)) %>% 
 summarize(caserate=round(mean(case_by_10k),2) ) %>% 
  group_by(name) %>% rename(City=name) %>%  formattable(list(align=c("l","r"),caserate=color_bar("lightblue")))

```

```{r graph, echo=FALSE,  message=FALSE, warning=FALSE}
end <- as_date(Sys.Date())
a1 %>% filter( id %in% c("Pleasant Hill","Martinez")) %>% ggplot(aes(date,cases)) + 
        facet_wrap(~id,ncol=1)  +
        geom_ma(ma_fun = EMA, n = 7,show.legend = T,linetype = "solid") + 
        coord_x_date(xlim = c(end - weeks(85), end))  + 
        theme_tq() + xlab("") + ylab("Daily Cases") + labs(title = "COVID 19 Historical Trend",
                                      caption = "Data source: LA Times; 7 day Average")
```


```{r graph2, echo=FALSE,  message=FALSE, warning=FALSE}
end <- as_date(Sys.Date())
a1 %>% filter( date > '2021-07-01',id %in% c("Pleasant Hill","Martinez","Concord","Richmond")) %>%
  rename(City=name) %>% ggplot(aes(date,case_by_10k,col=City,group=City)) + 
        geom_ma(ma_fun = EMA, n = 7,show.legend = T,linetype = "solid") + 
        coord_x_date(xlim = c(end - weeks(12), end))  + 
        theme_tq() + xlab("") +ylab("Case Rate per 10k") + labs(title = "COVID Case Rate Comparison",
                                      caption = "Data source: LA Times; 7 day Average")
```

*List of useful websites*

* [Contra Costa County Site](https://www.coronavirus.cchealth.org/dashboard)

* [LA Times Dashboard](https://www.latimes.com/projects/california-coronavirus-cases-tracking-outbreak/)

* [New York Times Dashboard](https://www.nytimes.com/interactive/2021/us/covid-cases.html)

* [California Public Dashboard](https://public.tableau.com/views/COVID-19PublicDashboard/Covid-19Public)

* [California Department of Public Health](https://www.cdph.ca.gov/Programs/CID/DCDC/Pages/Immunization/ncov2019.aspx) Was a place to look for positivity rates

* [IHME model](https://covid19.healthdata.org/united-states-of-america/california) is a good place to go for projections, as we blend this model into our work at KP  


